---
title: "Analyse questionnaire TF/PTF"
format: 
  html:
    embed-resources: true
knitr: 
  opts_chunk: 
    echo: false
    warning: false
    message: false
---

```{r}
#| label: packages
library(tidyverse)
library(googlesheets4)
```

This quarto report shows how the data from the questionnaire can be extracted and printed. 
Further analysis of the literature findings can proceed from here onwards. 
The data are stored in a googlesheets and you can use the `googlesheets4` package to extract them. 
Importing the data can be set up with a user-defined wrapper function.

```{r}
# interactive: authorize to get access to the googlesheet
gs4_auth()

source(here::here("source/R/import-data-questionnaire.R"))

url_sheet <- paste0("https://docs.google.com/spreadsheets/d/",
                    "13Qcj2Eg_oI9aUy7vL_34XdF-oucMppBdhk2w70AQMHk/",
                    "edit?gid=1214981089#gid=1214981089")

tf_ptf_review <- import_data_questionaire(url_sheet)
```

<br>

@fig-summaryreview displays the number of TF/PTF that have been reviewed.

```{r}
#| label: fig-summaryreview
#| fig-cap: Number of reviewed TF/PTF per soildescriptor

tf_ptf_review %>%
  summarise(.by = c(soildescriptor, tf_or_ptf), N = n()) %>%
  ggplot(aes(fct_reorder(soildescriptor, -N), N, fill = tf_or_ptf)) + 
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "count", fill = "")
```



